---
title: "Test: Outputs of Seurat standard pipeline"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

-   Tested pipeline:

`NormalizeData() %>% FindVariableFeatures() %>% ScaleData() %>% RunPCA() %>% RunUMAP(dims = 1:30)`

-   All parameters that weren't mentioned above were kept defaults.

-   Run the pipeline on two independent devices (`DESKTOP-5EA6KQM` and `ubuntu` as the hostnames), using the exactly same input and the same docker image.

```{r}
library(Seurat)
library(dplyr)
```

## Use original Seurat

```{r}
obj1 <- readRDS("../output/obj_std_DESKTOP-5EA6KQM_9629.Rds")
obj2 <- readRDS("../output/obj_std_ubuntu_254512.Rds")
```

### UMAP

-   The umap outputs were not reproducible!

```{r}
umap1 <- obj1[['umap']]@cell.embeddings
umap2 <- obj2[['umap']]@cell.embeddings
print(identical(umap1, umap2))
```

```{r}
library(patchwork)
p1 <- DimPlot(obj1, group.by = "Final_anno", label = T) + NoLegend()
p2 <- DimPlot(obj2, group.by = "Final_anno", label = T) + NoLegend()
p1 + p2
```

### Variable features

-   The variable features were identical!

```{r}
print(all.equal(VariableFeatures(obj1), VariableFeatures(obj2)))
```

### Scaled data

-   The scaled data were also identical!

```{r}
cm1 <- obj1[['RNA']]@scale.data
cm2 <- obj2[['RNA']]@scale.data
cm2 <- cm2[rownames(cm1), ]
print(all.equal(cm1, cm2))
```

```{r}
print(identical(cm1, cm2))
```

### PCA

-   The PCA outputs were the main source of differences!

```{r}
pc1 <- obj1[['pca']]@cell.embeddings
pc2 <- obj2[['pca']]@cell.embeddings
print(all.equal(pc1, pc2))
```

```{r}
gc(reset = TRUE)
```

## Use modified Seurat

-   In the original Seurat, `RunPCA()` use `irlba::irlba()` to calculate singular values. In the modified version, I replaced it with `RSpectra::svds()`.

`pca.results <- RSpectra::svds(A = object, k = npcs, ...)`

`pca.results <- RSpectra::svds(A = t(x = object), k = npcs, ...)`

```{r}
obj1 <- readRDS("../output/obj_std_modify_DESKTOP-5EA6KQM_9702.Rds")
obj2 <- readRDS("../output/obj_std_modify_ubuntu_254641.Rds")
gc(reset = TRUE)
```

### UMAP

-   The umap outputs were identical! Hurray!

```{r}
umap1 <- obj1[['umap']]@cell.embeddings
umap2 <- obj2[['umap']]@cell.embeddings
print(identical(umap1, umap2))
```

```{r}
p1 <- DimPlot(obj1, group.by = "Final_anno", label = T) + NoLegend()
p2 <- DimPlot(obj2, group.by = "Final_anno", label = T) + NoLegend()
p1 + p2
```

```{r}
cm1 <- obj1[['RNA']]@scale.data
cm2 <- obj2[['RNA']]@scale.data
cm2 <- cm2[rownames(cm1), ]
print(identical(cm1, cm2))
```

### PCA

-   The PCA outputs also passed `all.equal()`!

```{r}
pc1 <- obj1[['pca']]@cell.embeddings
pc2 <- obj2[['pca']]@cell.embeddings
print(all.equal(pc1, pc2))
```

-   But did not pass `identical()`! Whatever, it dosen't matter anymore.

```{r}
print(identical(pc1, pc2))
```
